---
title: "MMPCA - A package for the clustering of count data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MMPCA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
set.seed(42)
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MMPCA)
library(aricode)
```

## Description

MMPCA is a package to perform clustering of count data based on the *mixture of mutinomial PCA* model. It integrates a dimension reduction aspect by factorizing the multinomial parameters in a latent space, like *Latent Dirichlet Allocation* of Blei et. al.

## Dataset

The package contains attached data in **BBCmsg**. It consists in 4 text document already preprocessed with the **tm** package. It is mostly useful for the `simulate_BBC()` function.  
```{r , eval=FALSE}
data("BBCmsg")
```

## Mathematical background

## Demonstration for document clustering

Start by generating data from the MMPCA model with a particular $\theta^\star$ and $\beta^\star$. For more detail, check experimental section of the paper.
```{r generate-data, echo=TRUE}
data("BBCmsg")
N = 50
L = 200
simu <- simulate_BBC(N, L, epsilon = 0, lambda = 1)
Ytruth <- simu$Ytruth
```

Then perform cluster
```{r mmpca}
res <- mmpca_clust(simu$dtm.full, Q = 6, K = 4,
                          Yinit = 'random',
                          method = 'CVEM',
                          max.epochs = 10,
                          keep = 1,
                          verbose = 1)
```

### Results analysis

```{r clustering-results, echo=TRUE, include=TRUE}
tab <- knitr::kable(table(res@clustering, Ytruth), format = 'markdown')
print(tab)
cat('Final ARI is ', aricode::ARI(res@clustering, Ytruth))
```

Other visualization are also accessible from the `plot` function. Which takes several arguments
```{r plot-results-topics, fig.dim=c(5,5)}
ggtopics <- plot(res, show = 'topics')
print(ggtopics)
```
```{r plot-results-bound, fig.dim=c(5,5), echo=TRUE, include=TRUE}
ggbound <- plot(res, type = 'bound')
print(ggbound)
```

