---
title: "MoMPCA - A package for the clustering of count data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MoMPCA}
  %\VignetteEngine{knitr::knitr}
  %\usepackage[utf8]{inputenc}
---

```{r}
set.seed(42)
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MoMPCA)
library(aricode)
```

## Description

MMPCA is a package to perform clustering of count data based on the *mixture of multinomial PCA* model. It integrates a dimension reduction aspect by factorizing the multinomial parameters in a latent space, like *Latent Dirichlet Allocation* of Blei et. al. It specially conceived for low sample high-dimensional data. Due to the intensive nature of the greedy algorithm, it is not suited for large sample size.

## Dataset

The package contains attached data in **BBCmsg**. It consists in 4 text document already preprocessed with the **tm** package. It is mostly useful for the `simulate_BBC()` function.  
```{r , eval=FALSE}
data("BBCmsg")
```


## Demonstration for document clustering

Start by generating data from the MMPCA model with a particular $\theta^\star$ and $\beta^\star$. For more detail, check experimental section of the paper.
```{r generate-data, echo=TRUE}
N = 200
L = 250
simu <- simulate_BBC(N, L, epsilon = 0, lambda = 1)
Ytruth <- simu$Ytruth
```

Then perform clustering
```{r mmpca}
t0 <- system.time(res <- mmpca_clust(simu$dtm.full, Q = 6, K = 4,
                          Yinit = 'random',
                          method = 'BBCVEM',
                          max.epochs = 7,
                          keep = 1,
                          verbose = 2,
                          nruns = 2,
                          mc.cores = 2)
               )
print(t0)
```

### Results analysis

```{r clustering-results, echo=TRUE, include=TRUE}
tab <- knitr::kable(table(res@clustering, Ytruth), format = 'markdown')
print(tab)
cat('Final ARI is ', aricode::ARI(res@clustering, Ytruth))
```

Other visualization are also accessible from the `plot` function. Which takes several arguments
```{r condition-eval-plot, echo=F}
cond = requireNamespace("ggplot2", quietly = TRUE) & requireNamespace("dplyr", quietly = TRUE) & requireNamespace("tidytext", quietly = TRUE)
```

```{r plot-results-topics, fig.dim=c(5,5), eval=cond}
ggtopics <- plot(res, type = 'topics')
print(ggtopics)
```
```{r plot-results-bound, fig.dim=c(5,5), echo=TRUE, include=TRUE}
ggbound <- plot(res, type = 'bound')
print(ggbound)
```

## Model selection

The package contains a convenient wrapper around `mmpca_clust()` which performs model selection over a grid of values for $(K,Q)$. Here is the results for `Qs = 5:7` and `Ks = 3:5`.

```{r model-selection, eval=F}
t1 <- system.time(res <- mmpca_clust_modelselect(simu$dtm.full, Qs = 5:7, Ks = 3:5,
                          Yinit = 'kmeans_lda',
                          init.beta = 'lda',
                          method = 'BBCVEM',
                          max.epochs = 7,
                          nruns = 3,
                          verbose = 1)
               )
print(t1)
best_model = res$models
print(best_model)
```


